Lessons Learned for JWST Transiting Planet Time Series from Ground-based Studies of the NIRCam Detectors

### 2019-01-16 ms.tex
added rectangular background-subtracted time series.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
\caption{{\it Top:} A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
The standard deviation decreases as the number of groups up the ramp becomes more numerous.
This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}
\end{figure}

>>>>

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser.pdf}
\caption{A variety of subarrays in the OTIS stability tests were read out with similar integration times (32 to 39 seconds) to compare relative precision of the read modes. 
The time series are ordered vertically in increasing frame duration (and decreasing number of groups up the ramp) toward the bottom.
The standard deviation decreases as the number of groups up the ramp becomes more numerous.
This is likely related to correlated 1/f noise in the horizontal direction that is averaged out by more reads up the ramp.}\label{fig:OTISsubarrays}
\end{figure}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{fullframe_background_sub_compare_tser_tools.pdf}
\caption{An experiment with circular background-subtracted photometry shows dramatically improved precisions over raw aperture sums in Figure \ref{fig:OTISsubarrays}.
Additionally, a median subtraction of all background pixels per row improves the precision.}\label{fig:OTISSubConfigCircularAp}
\end{figure}

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.5\columnwidth]{subarray_config_tser_backsub_rect.pdf}
\caption{With rect backub.}\label{fig:OTISRectBacksub}
\end{figure}
